% ============================================================================
%  BasaBondhu — Complete Project Documentation
%  Compiled with: pdflatex documentation.tex
% ============================================================================

\documentclass[12pt, a4paper, oneside]{report}

% ── Packages ────────────────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{listings}
\usepackage{float}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{amsmath}
\usepackage{caption}

% ── Colour Definitions ─────────────────────────────────────────────────────
\definecolor{primary}{HTML}{C9952B}
\definecolor{darkbg}{HTML}{1A1A2E}
\definecolor{codeblue}{HTML}{4A90D9}
\definecolor{codegray}{HTML}{5F6368}
\definecolor{codebg}{HTML}{F5F5F5}
\definecolor{linkcolor}{HTML}{1A73E8}

% ── Hyperref Setup ──────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  linkcolor=darkbg,
  urlcolor=linkcolor,
  citecolor=primary,
  pdftitle={BasaBondhu -- Complete Project Documentation},
  pdfauthor={BasaBondhu Development Team},
  pdfsubject={Project Documentation},
  pdfkeywords={BasaBondhu, Next.js, React, Dhaka, Housing, Renter Intelligence}
}

% ── Listings Configuration ──────────────────────────────────────────────────
\lstset{
  backgroundcolor=\color{codebg},
  basicstyle=\ttfamily\small,
  keywordstyle=\color{codeblue}\bfseries,
  commentstyle=\color{codegray}\itshape,
  stringstyle=\color{primary},
  breaklines=true,
  frame=single,
  rulecolor=\color{codegray!30},
  numbers=left,
  numberstyle=\tiny\color{codegray},
  numbersep=8pt,
  tabsize=2,
  showstringspaces=false,
  captionpos=b
}

% ── Header / Footer ────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textcolor{codegray}{\leftmark}}
\fancyhead[R]{\small\textcolor{primary}{BasaBondhu}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

% ── Section Formatting ──────────────────────────────────────────────────────
\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries\color{darkbg}}
  {\chaptertitlename\ \thechapter}{20pt}{\Huge}
\titlespacing*{\chapter}{0pt}{0pt}{20pt}

% ── Custom Commands ─────────────────────────────────────────────────────────
\newcommand{\filepath}[1]{\texttt{\small\color{codeblue}#1}}
\newcommand{\component}[1]{\textbf{\color{darkbg}#1}}
\newcommand{\apiendpoint}[1]{\texttt{\small\color{primary}#1}}
\newcommand{\typename}[1]{\texttt{\small\color{codeblue}#1}}

% ============================================================================
\begin{document}

% ── Title Page ──────────────────────────────────────────────────────────────
\begin{titlepage}
\centering
\vspace*{2cm}

{\Huge\bfseries\textcolor{darkbg}{BasaBondhu}\par}
\vspace{0.5cm}
{\Large\textcolor{primary}{Guided House-Hunting in Bangladesh}\par}
\vspace{1.5cm}

{\large\textcolor{codegray}{Complete Project Documentation}\par}
\vspace{0.3cm}
{\textcolor{codegray}{Version 0.1.0}\par}

\vfill

{\large\textcolor{codegray}{From messy listings to 3 homes worth visiting.\\
Check costs, trade-offs, and call scripts.}\par}

\vspace{2cm}

{\textcolor{codegray}{BasaBondhu Development Team}\par}
{\textcolor{codegray}{\today}\par}
\end{titlepage}

% ── Table of Contents ───────────────────────────────────────────────────────
\tableofcontents
\newpage

% ============================================================================
% CHAPTER 1 — INTRODUCTION
% ============================================================================
\chapter{Introduction}

\section{What is BasaBondhu?}

BasaBondhu (literally ``House Friend'' in Bangla) is a \textbf{renter intelligence platform} purpose-built for house-hunters navigating the notoriously opaque Dhaka rental market. The platform transforms unstructured, scattered Facebook group listings into structured, scored, and actionable intelligence.

BasaBondhu is \emph{not} a listing aggregator. It is a guided decision-making companion that helps users:

\begin{itemize}[leftmargin=2em]
  \item Parse and structure messy Bengali/Banglish Facebook listing text.
  \item Score and rank flats against personal budget, commute, and lifestyle requirements.
  \item Surface hidden costs and ambiguities that landlords or brokers routinely omit.
  \item Generate phone call scripts and physical visit checklists before even leaving the house.
  \item Compile a print-ready assessment report to carry during flat visits.
\end{itemize}

\section{Target Users}

\begin{longtable}{p{3.5cm} p{10cm}}
\toprule
\textbf{User Persona} & \textbf{Description} \\
\midrule
\endhead
Rafi \& Mita (Demo Couple) & Moving from Cumilla to Dhaka. Rafi works in Banani, Mita works from home. Seeking a safe, family-friendly flat. \\
\midrule
Nusrat (Female Student) & University student looking for a secure female-only sublet room or hostel near Dhanmondi. Extremely budget-conscious. \\
\midrule
Abrar (Single Professional) & Software engineer working in Mohakhali, looking for a bachelor-friendly shared room or small flat. Prefers direct owners. \\
\midrule
Haque Family (4 Members) & Shifting to be closer to their children's school in Mohammadpur. High importance on gas line and school access. \\
\midrule
Tasnim (Working Woman) & Corporate manager relocated to Gulshan/Banani. Security, generator backup, late-night entry access, and lift are absolute priorities. \\
\midrule
Arafat (Group Flatmates) & Group of 3 bachelors pooling rent in Bashundhara/Badda. Budget per head is low but collectively they afford a decent flat. \\
\bottomrule
\end{longtable}

\section{Technology Stack}

\begin{longtable}{p{4cm} p{9cm}}
\toprule
\textbf{Technology} & \textbf{Role} \\
\midrule
\endhead
Next.js 16 (App Router) & Full-stack React framework with file-system routing, server components, and API routes. \\
\midrule
React 19 & UI rendering with hooks, context, and memoisation. \\
\midrule
TypeScript 5 & Static type safety across the entire codebase. \\
\midrule
Tailwind CSS 4 & Utility-first CSS framework for responsive, premium design. \\
\midrule
Framer Motion 12 & Declarative animations, page transitions, and micro-interactions. \\
\midrule
Leaflet + React-Leaflet 5 & Interactive 2D maps with custom marker badges for Dhaka areas. \\
\midrule
Lucide React & Icon library used across all UI components. \\
\midrule
Clsx + Tailwind-Merge & Conditional class name merging utilities. \\
\midrule
Google Fonts (Inter, Cormorant Garamond) & Premium typography pairing: Inter for UI, Cormorant Garamond for headings. \\
\bottomrule
\end{longtable}


% ============================================================================
% CHAPTER 2 — ARCHITECTURE
% ============================================================================
\chapter{Architecture Overview}

\section{High-Level Flow}

The application follows a linear yet branching pipeline:

\begin{enumerate}[leftmargin=2em]
  \item \textbf{Landing Page} --- Cinematic entrance with scroll-driven video simulation and dual entry paths.
  \item \textbf{Entry Path A: Guided Wizard} --- Collect household details, budget, commute anchors, and deal-breakers.
  \item \textbf{Entry Path B: Facebook Fetcher} --- Paste a Facebook URL, crawl the listing, and auto-extract structured data.
  \item \textbf{Scan Simulator} --- Animated radar scanning simulation that matches, filters, and scores listings.
  \item \textbf{Portal Dashboard} --- Multi-tab workspace containing all analysis tools.
  \item \textbf{Assessment Report} --- Compiled printable output of the entire analysis.
\end{enumerate}

\section{Directory Structure}

\begin{lstlisting}[language={}, caption={Project Directory Tree}]
basabondhu/
  app/
    layout.tsx              # Root layout with SearchProvider
    page.tsx                # Landing page entry
    globals.css             # Global CSS and design tokens
    portal/
      layout.tsx            # Portal tab navigation shell
      page.tsx              # Plan Search (main dashboard)
      parser/page.tsx       # Check Listing page
      fb-fetch/page.tsx     # Facebook Fetcher page
      compare/page.tsx      # Compare Homes page
      visit/page.tsx        # Prepare Visit page
      report/page.tsx       # Assessment Report page
      wizard/page.tsx       # Guided Matcher Wizard
    api/
      areas/                # Area data API
      compare/              # Comparison engine API
      demo/                 # Demo scan API
      facebook/fetch/       # Facebook crawler API
      harvester/            # Harvester data pipeline API
      listings/             # Listings data API
      parse/                # Text parser API
      report/               # Report generation API
      search/               # Search profile API
  components/
    LandingPage.tsx         # Cinematic landing page
    ScrollVideo.tsx         # Scroll-driven video simulation
    Wizard.tsx              # Guided matcher wizard
    FacebookFetcher.tsx     # Facebook link crawler UI
    ListingChecker.tsx      # Messy listing text checker
    AreaRecommendations.tsx # Area recommendation cards
    DemoScanAnimation.tsx   # Radar scan simulator
    ListingGrid.tsx         # Scored listing result grid
    DrawerMap.tsx           # Leaflet map wrapper
    DrawerMapInner.tsx      # Map markers and badges
    HiddenCostScopeRadar.tsx# Hidden cost visualisation
    ListingComparison.tsx   # Side-by-side comparison
    VisitPlanner.tsx        # Visit preparation workspace
    ReportPreview.tsx       # Assessment report compilation
    Navbar.tsx              # Top navigation bar
    Skeletons.tsx           # Loading skeleton components
    Typewriter.tsx          # Typing animation effect
    VerdictBadge.tsx        # Verdict indicator badge
    ErrorBoundary.tsx       # React error boundary
    PersonaIcons.tsx        # SVG persona icon set
    ModeSelector.tsx        # Mode selection component
    ProofRequestPanel.tsx   # Proof request UI panel
    MapScanner.tsx          # Map scanner wrapper
    MapScannerInner.tsx     # Map scanner core logic
    HousingProfileSummary.tsx # Profile summary card
  context/
    SearchContext.tsx        # Global state management
  lib/
    types.ts                 # Core TypeScript type definitions
    parser.ts                # Regex-based listing text parser
    scoring.ts               # Multi-factor scoring algorithm
    cost-calculator.ts       # First-month cost calculator
    domain/
      hidden-cost-sources.ts # Hidden cost type definitions
    data/
      areas.ts               # 13 Dhaka area profiles
      listings.ts            # Seed listing database
      messy-examples.ts      # Sample messy listing texts
      personas.ts            # Preset renter personas
    services/
      area-recommendation.service.ts
      checklist.service.ts
      compare.service.ts
      cost.service.ts
      demo-scan.service.ts
      hidden-cost-scope.service.ts
      listing-parser.service.ts
      openrouter.service.ts
      question.service.ts
      recommendation.service.ts
      report.service.ts
      scoring.service.ts
      search-profile.service.ts
    repositories/
      area.repository.ts
      listing.repository.ts
    utils/
      currency.ts
      text-normalizer.ts
    harvester/               # Data harvester pipeline
      chunk-builder.service.ts
      dedupe.service.ts
      enrichment.service.ts
      extractor.service.ts
      freshness.service.ts
      google-sheet-importer.service.ts
      harvester-orchestrator.service.ts
      listing-mapper.ts
      offer-snapshot.service.ts
      openrouter-extractor.service.ts
      partner-csv-importer.service.ts
      public-url-ingestion.service.ts
      quality.service.ts
      raw-document.service.ts
      source-registry.service.ts
      structured-listing-builder.service.ts
      text-normalizer.service.ts
      user-paste-ingestion.service.ts
    types/
      harvester.ts           # Harvester-specific types
\end{lstlisting}


\section{State Management --- SearchContext}

All application state is managed through a single React Context provider (\filepath{context/SearchContext.tsx}) that wraps the entire application. The context maintains:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Search Profile} --- User preferences, budget, commute anchors, and deal-breakers.
  \item \textbf{Scored Listings} --- Dynamically computed ranked listings based on the active profile.
  \item \textbf{Comparison Selections} --- Up to 3 listings selected for side-by-side comparison.
  \item \textbf{Scan State} --- Progress tracking for the scan simulator animation.
  \item \textbf{Checker State} --- Messy listing checker input, parsed output, and manual overrides.
  \item \textbf{Facebook Fetcher State} --- URL, crawled text, parsed data, and crawl logs.
  \item \textbf{View Mode} --- Toggles between ``landing'' and ``portal'' views.
  \item \textbf{Active Tab} --- Current portal tab (search, check, compare, visit).
  \item \textbf{LocalStorage Persistence} --- All state is serialised and restored from \texttt{localStorage} across page reloads.
\end{itemize}


% ============================================================================
% CHAPTER 3 — LANDING PAGE
% ============================================================================
\chapter{Landing Page}

\section{Overview}

The landing page (\filepath{components/LandingPage.tsx}) serves as the cinematic entrance to BasaBondhu. It is designed with high-contrast typography, premium gold gradients, and an immersive scroll-driven experience.

\section{Scroll-Driven Video Simulation}

\component{ScrollVideo.tsx} implements a canvas-driven, frame-by-frame scroll animation that renders a sequence of pre-loaded Dhaka cityscape images. As the user scrolls, the canvas progresses through the frames, creating a cinematic video-like effect without requiring actual video playback.

\subsection{How to Use}

\begin{enumerate}[leftmargin=2em]
  \item Open the application at the root URL (\texttt{/}).
  \item Scroll down slowly to experience the frame-by-frame video simulation.
  \item The animation progresses proportionally to scroll depth.
\end{enumerate}

\section{Navigation Entry Points}

The landing page presents two primary call-to-action paths:

\begin{enumerate}[leftmargin=2em]
  \item \textbf{Start Planning (Guided Wizard)} --- Routes the user to the Guided Matcher Wizard at \texttt{/portal/wizard} where they configure their renter profile step by step.
  \item \textbf{Crawl a Listing (Facebook Fetcher)} --- Routes the user to the Facebook Fetcher at \texttt{/portal/fb-fetch} where they can paste a Facebook listing URL for instant analysis.
\end{enumerate}

\section{Design Elements}

\begin{itemize}[leftmargin=2em]
  \item Gold accent colour (\texttt{\#C9952B}) used for brand highlights and CTAs.
  \item Serif/sans-serif font pairing: Cormorant Garamond for hero headings, Inter for body text.
  \item Dark gradient overlays on imagery for text readability.
  \item Framer Motion animations for fade-in and slide-up transitions.
  \item Fully responsive layout adapting to mobile, tablet, and desktop viewports.
\end{itemize}


% ============================================================================
% CHAPTER 4 — GUIDED MATCHER WIZARD
% ============================================================================
\chapter{Guided Matcher Wizard}

\section{Overview}

The Guided Matcher Wizard (\filepath{components/Wizard.tsx}) collects all necessary information about a prospective renter through an animated multi-step form. This data is used to build a \typename{SearchProfile} that drives all downstream scoring and matching.

\section{Steps}

\subsection{Step 1: Household Details}

Collects the user's household configuration. Options include:

\begin{longtable}{p{4cm} p{9cm}}
\toprule
\textbf{Household Type} & \textbf{Description} \\
\midrule
\endhead
\texttt{family} & Full family unit (parents + children). \\
\texttt{couple} & Married or unmarried couple. \\
\texttt{bachelor} & Single male living alone or sharing with others. \\
\texttt{student} & University or college student (male or female). \\
\texttt{working-woman} & Female professional living alone or sharing with females. \\
\texttt{group} & Group of flatmates (typically 2--4 bachelors). \\
\texttt{single-professional} & Single working professional (gender-neutral). \\
\bottomrule
\end{longtable}

Also collects the \textbf{Looking For} preference:

\begin{itemize}[leftmargin=2em]
  \item \texttt{full-flat} --- An entire flat/apartment.
  \item \texttt{room-sublet} --- A single room in a shared flat.
  \item \texttt{checking-listing} --- Just checking/analysing a listing (no active search).
\end{itemize}

\subsection{Step 2: Financial Boundaries}

\begin{itemize}[leftmargin=2em]
  \item \textbf{Monthly Budget} (\texttt{budgetMonthly}) --- Maximum monthly rent the user can afford (in BDT).
  \item \textbf{Max First Month Cash} (\texttt{maxFirstMonthCash}) --- Total available upfront cash including advance deposit, first month rent, broker fee, moving cost, and service charge.
\end{itemize}

\subsection{Step 3: Commute Anchors}

Users specify their primary commute destinations (office, university, school). Each anchor is defined by:

\begin{itemize}[leftmargin=2em]
  \item A \textbf{label} (e.g., ``Rafi's Office'', ``University'', ``School'').
  \item An \textbf{area} selected from 13 supported Dhaka areas.
\end{itemize}

Optional fields include: husband's job location, wife's job location, child's school location, healthcare proximity needs, car ownership, preferred flat facing direction (south/east/west/north), nearby market preference, and environment preference (quiet/commercial/any).

\subsection{Step 4: Deal Breakers \& Priorities}

\paragraph{Priorities} (ranked preferences):

\begin{multicols}{2}
\begin{itemize}[leftmargin=1em]
  \item \texttt{commute} --- Short commute
  \item \texttt{rent} --- Low rent
  \item \texttt{school} --- Near schools
  \item \texttt{safety} --- Safe neighbourhood
  \item \texttt{gas} --- Gas line available
  \item \texttt{lift} --- Lift/elevator
  \item \texttt{generator} --- Generator backup
  \item \texttt{no-waterlogging} --- Flood-free area
  \item \texttt{bachelor-friendly} --- Bachelor allowed
  \item \texttt{family-friendly} --- Family preferred
  \item \texttt{quiet-area} --- Quiet surroundings
  \item \texttt{direct-owner} --- No broker
\end{itemize}
\end{multicols}

\paragraph{Deal Breakers} (hard disqualifiers):

\begin{multicols}{2}
\begin{itemize}[leftmargin=1em]
  \item \texttt{broker} --- Broker involvement
  \item \texttt{high-advance} --- 3+ months advance
  \item \texttt{family-only} --- Family-only policy
  \item \texttt{no-lift} --- No lift
  \item \texttt{no-gas} --- No gas connection
  \item \texttt{heavy-waterlogging} --- High flood risk
  \item \texttt{far-from-transport} --- Far from transit
\end{itemize}
\end{multicols}

\section{Persona Quick Selectors}

Instead of filling the wizard manually, users can select from pre-built renter personas. Each persona pre-fills the entire \typename{SearchProfile} with realistic Dhaka renter parameters. Personas are defined in \filepath{lib/data/personas.ts} and include custom SVG icons rendered by \filepath{components/PersonaIcons.tsx}.

\subsection{How to Use}

\begin{enumerate}[leftmargin=2em]
  \item Navigate to the Portal (\texttt{/portal}).
  \item If no profile exists, the persona selection grid is displayed automatically.
  \item Click any persona card to instantly load their profile.
  \item Alternatively, click ``Custom Guided Matcher'' to start the step-by-step wizard.
\end{enumerate}


% ============================================================================
% CHAPTER 5 — FACEBOOK FETCHER
% ============================================================================
\chapter{Facebook Crawler \& Structuring Fetcher}

\section{Overview}

The Facebook Fetcher (\filepath{components/FacebookFetcher.tsx}) allows users to paste a Facebook listing URL and receive structured, analysed data extracted from the raw post caption.

\section{Architecture}

\subsection{Frontend --- FacebookFetcher Component}

The UI provides:

\begin{itemize}[leftmargin=2em]
  \item A URL input field with validation for Facebook domains.
  \item A real-time crawl log display showing each stage of the fetching process.
  \item Animated progress indicators during crawling.
  \item A structured data card displaying all extracted fields after parsing.
  \item A ``Start Scanning Similar Homes Now'' button that auto-fills the extracted data into a \typename{SearchProfile} and triggers the scan simulator.
\end{itemize}

\subsection{Backend --- API Route}

The server-side route at \apiendpoint{/api/facebook/fetch} performs:

\begin{enumerate}[leftmargin=2em]
  \item Accepts a Facebook URL via POST request.
  \item Simulates a Googlebot user-agent header to bypass Facebook's preview restrictions.
  \item Extracts the raw post caption text from the HTML meta tags.
  \item Returns the un-truncated text content to the frontend.
\end{enumerate}

\section{Auto-Fill Extraction Engine}

After fetching raw text, the frontend invokes the regex-based parser (\filepath{lib/parser.ts}) to extract:

\begin{longtable}{p{4cm} p{9cm}}
\toprule
\textbf{Field} & \textbf{Extraction Method} \\
\midrule
\endhead
Area/Location & String matching against 13 known Dhaka areas. \\
\midrule
Rent & Regex patterns for ``28k'', ``28,000'', or ``rent/bhara'' labels. \\
\midrule
Bedrooms & Pattern ``N bed/bedroom/room'' extraction. \\
\midrule
Bathrooms & Pattern ``N bath/bathroom'' extraction. \\
\midrule
Tenant Preference & Keywords: ``family only'', ``bachelor'', ``female'', ``student'', ``any''. \\
\midrule
Advance Months & Pattern ``N month advance/security'' extraction. \\
\midrule
Lift & ``lift'' keyword presence/absence check. \\
\midrule
Generator & ``generator/gen backup/power backup'' keyword check. \\
\midrule
Gas Type & ``cylinder/LPG'' vs ``line gas/Titas'' differentiation. \\
\midrule
Service Charge & Amount extraction or ``extra/included'' classification. \\
\midrule
Broker Fee & ``direct owner'' vs ``broker fee'' detection. \\
\midrule
Availability & Date/month extraction from availability keywords. \\
\bottomrule
\end{longtable}

The parser also supports \textbf{Bangla} keywords (e.g., ``bhara/ভাড়া'', ``ব্যাচেলর'', ``সিলিন্ডার'', ``লাইন গ্যাস'').

\section{Scanning Trigger}

Clicking ``Start Scanning Similar Homes Now'' performs:

\begin{enumerate}[leftmargin=2em]
  \item Constructs a \typename{SearchProfile} from the parsed fields.
  \item Calls \texttt{planSearch()} on the SearchContext to initialise the profile.
  \item Activates the scan simulator animation.
  \item Redirects to the portal dashboard with matched results.
\end{enumerate}


% ============================================================================
% CHAPTER 6 — LISTING CHECKER
% ============================================================================
\chapter{Raw Listing Checker}

\section{Overview}

The Listing Checker (\filepath{components/ListingChecker.tsx}) provides an alternate workflow for analysing any arbitrary listing text. Users paste raw text from Facebook groups, WhatsApp messages, or broker descriptions.

\section{Features}

\subsection{Text Parsing}

The component sends the pasted text to \apiendpoint{/api/parse} which invokes \filepath{lib/parser.ts} to extract structured fields. It also accepts optional \textbf{manual overrides} for:

\begin{itemize}[leftmargin=2em]
  \item Rent amount
  \item Advance months
  \item Service charge
  \item Broker fee
\end{itemize}

These overrides allow users to correct the parser's output when they have additional information.

\subsection{Red Flags \& Warning Engine}

After parsing, the checker surfaces warning bullet points for common issues:

\begin{itemize}[leftmargin=2em]
  \item ``Bachelor restrictions apply''
  \item ``Unspecified service charge''
  \item ``No gas pipeline mentioned''
  \item ``High advance requirement (3+ months)''
  \item ``Broker fee applicable''
  \item ``Missing location information''
\end{itemize}

\subsection{Suitability Verdict Badge}

The \component{VerdictBadge} component (\filepath{components/VerdictBadge.tsx}) renders a colour-coded badge:

\begin{longtable}{p{3cm} p{3cm} p{7cm}}
\toprule
\textbf{Verdict} & \textbf{Colour} & \textbf{Meaning} \\
\midrule
\endhead
\texttt{visit} & Green & This listing is worth a physical visit. \\
\texttt{maybe} & Yellow/Amber & Potentially suitable but needs clarification. \\
\texttt{call-first} & Orange & Hidden costs or ambiguities detected --- call before visiting. \\
\texttt{avoid} & Red & Deal-breakers triggered or critically poor fit. \\
\bottomrule
\end{longtable}

\subsection{Messy Examples Library}

The checker includes a library of sample messy listing texts (\filepath{lib/data/messy-examples.ts}) that users can load with a single click to test the parser. These examples replicate real-world Facebook group posts in Banglish.


% ============================================================================
% CHAPTER 7 — SCORING ENGINE
% ============================================================================
\chapter{Multi-Factor Scoring Engine}

\section{Overview}

The scoring engine (\filepath{lib/scoring.ts}) evaluates every listing against the user's \typename{SearchProfile} using a weighted multi-factor algorithm. Each listing receives a composite score out of 100.

\section{Scoring Factors}

\subsection{1. Budget Fit (Weight: 25\%)}

\begin{equation}
\text{budgetFit} = \max\!\left(0,\; 100 - \frac{(\text{rent} - \text{budgetMonthly})}{\text{budgetMonthly}} \times 200\right)
\end{equation}

If rent is within budget, the score is 100. Exceeding the budget results in a steep penalty.

\subsection{2. First Month Fit (Weight: 10\%)}

\begin{equation}
\text{firstMonthFit} = \max\!\left(0,\; 100 - \frac{(\text{totalFirstMonthCost} - \text{maxFirstMonthCash})}{\text{maxFirstMonthCash}} \times 150\right)
\end{equation}

Evaluates whether the user can afford the total move-in cost (rent + advance + service charge + broker fee + moving estimate).

\subsection{3. Commute Fit (Weight: 20\%)}

Uses a 13$\times$13 \textbf{commute compatibility matrix} mapping all supported Dhaka areas. Scores range from 100 (same area) to 20 (very poor connectivity). If multiple commute anchors are defined, the average score is used.

Supported areas: Banasree, Badda, Merul Badda, Mohakhali, Tejgaon, Mohammadpur, Lalmatia, Mirpur, Uttara, Bashundhara, Dhanmondi, Banani, Gulshan.

\subsection{4. Household Fit (Weight: 15\%)}

Cross-references the user's \texttt{householdType} with the listing's \texttt{tenantPreference}:

\begin{itemize}[leftmargin=2em]
  \item A bachelor looking at a ``family only'' listing scores 10/100.
  \item A bachelor looking at a ``female'' listing scores 0/100 (strict fail).
  \item A family looking at a ``family'' listing scores 100/100.
  \item Listings with ``any'' preference score 75--80/100 for most types.
\end{itemize}

\subsection{5. Hidden Cost Penalty (Weight: 15\%)}

For each hidden cost scope detected:
\begin{itemize}[leftmargin=2em]
  \item \textbf{Critical} seriousness: $-25$ points
  \item \textbf{High} seriousness: $-15$ points
  \item \textbf{Medium} seriousness: $-5$ points
\end{itemize}
Capped at a maximum penalty of 100.

\subsection{6. Utility Clarity (Weight: 5\%)}

\begin{itemize}[leftmargin=2em]
  \item Clear utility information: 100
  \item Partial information: 60
  \item Unclear: 20
\end{itemize}

\subsection{7. Waterlogging Risk (Weight: 5\%)}

\begin{itemize}[leftmargin=2em]
  \item Low risk: 100
  \item Unknown: 70
  \item Medium risk: 50
  \item High risk: 10
\end{itemize}

\subsection{8. Listing Trust (Weight: 5\%)}

A trust score starting at 60, adjusted by:
\begin{itemize}[leftmargin=2em]
  \item +15 if rent is specified.
  \item +15 if area is specified.
  \item +10 if good points are present.
  \item $-20$ if more than 3 red flags exist.
\end{itemize}

\section{Dynamic Weight Adjustments}

Users can toggle adjustments that dynamically re-weight the scoring:

\begin{longtable}{p{4cm} p{9cm}}
\toprule
\textbf{Adjustment} & \textbf{Effect} \\
\midrule
\endhead
\texttt{shorter-commute} & Commute weight increases to 40\%; budget and household weights decrease. \\
\midrule
\texttt{lower-rent} & Budget weight increases to 40\%; commute and hidden cost weights decrease. \\
\midrule
\texttt{avoid-broker} & Applies a $-40$ point direct penalty to broker-sourced listings. \\
\midrule
\texttt{avoid-waterlogging} & Applies a $-50$ penalty for high waterlogging risk, $-25$ for medium. \\
\bottomrule
\end{longtable}

\section{Deal Breaker Logic}

If any deal-breaker is triggered, the listing is automatically assigned the \textbf{avoid} verdict regardless of score:

\begin{itemize}[leftmargin=2em]
  \item \texttt{broker}: Listing source is ``broker''.
  \item \texttt{high-advance}: Advance months $\geq 3$.
  \item \texttt{family-only}: Family-only preference when user is bachelor/student.
  \item \texttt{no-lift}: No lift available.
  \item \texttt{no-gas}: Gas type is unknown.
  \item \texttt{heavy-waterlogging}: Waterlogging risk is ``high''.
\end{itemize}

\section{Verdict Assignment}

\begin{longtable}{p{3cm} p{10cm}}
\toprule
\textbf{Verdict} & \textbf{Condition} \\
\midrule
\endhead
\texttt{avoid} & Deal-breaker triggered, total $< 40$, or household fit $= 0$. \\
\texttt{visit} & Total $\geq 75$ and no high/critical hidden cost scopes. \\
\texttt{maybe} & Total $\geq 55$ and $\leq 2$ high-severity scopes. \\
\texttt{call-first} & Everything else --- clarification needed before visiting. \\
\bottomrule
\end{longtable}

\section{Generated Contextual Outputs}

Each scored listing also produces:

\begin{itemize}[leftmargin=2em]
  \item \textbf{whyItFits} --- A human-readable explanation of suitability.
  \item \textbf{biggestRisk} --- The single most significant risk factor.
  \item \textbf{questionsToAsk} --- A list of specific questions to ask the landlord/broker before visiting.
\end{itemize}


% ============================================================================
% CHAPTER 8 — FIRST MONTH COST CALCULATOR
% ============================================================================
\chapter{First Month Cost Calculator}

\section{Overview}

The cost calculator (\filepath{lib/cost-calculator.ts}) computes the total ``Day 1'' financial outlay required to move into a flat.

\section{Cost Components}

\begin{equation}
\text{Total} = \text{Rent} + (\text{Rent} \times \text{advanceMonths}) + \text{serviceCharge} + \text{brokerFee} + \text{movingEstimate}
\end{equation}

\subsection{Moving Cost Estimate}

Based on the rent class:

\begin{longtable}{p{4cm} p{4cm}}
\toprule
\textbf{Rent Range} & \textbf{Moving Estimate (BDT)} \\
\midrule
\endhead
$\leq$ 15,000 & 3,000 \\
$\leq$ 30,000 & 5,000 \\
$>$ 30,000 & 8,000 \\
\bottomrule
\end{longtable}

\section{Generated Warnings}

The calculator surfaces contextual warnings:

\begin{itemize}[leftmargin=2em]
  \item Unclear service charge --- could add 2,000--5,000 BDT/month.
  \item Unknown broker fee --- may add up to 1 month rent.
  \item High advance requirement (2+ months).
  \item Cylinder gas --- adds 1,500--2,500 BDT/month.
  \item Heavy waterlogging risk during monsoons.
\end{itemize}


% ============================================================================
% CHAPTER 9 — HIDDEN COST SCOPE RADAR
% ============================================================================
\chapter{Hidden Cost Scope Radar}

\section{Overview}

The Hidden Cost Scope Radar (\filepath{components/HiddenCostScopeRadar.tsx}) is a visual dashboard that surfaces all hidden, missing, unclear, or contradictory cost signals detected in a listing.

\section{Detection Engine}

The detection logic lives in \filepath{lib/services/hidden-cost-scope.service.ts}. It analyses the parsed listing, raw text, area profile, and user's search profile to detect scopes across 20 categories:

\begin{longtable}{p{5cm} p{8cm}}
\toprule
\textbf{Hidden Cost Source ID} & \textbf{Description} \\
\midrule
\endhead
\texttt{advance\_terms} & Advance payment amount and refund terms. \\
\texttt{service\_charge} & Monthly building service/maintenance charge. \\
\texttt{broker\_fee} & One-time broker or media fee. \\
\texttt{gas\_type} & Gas connection type (line vs cylinder). \\
\texttt{electricity\_billing} & Electricity meter type and billing method. \\
\texttt{water\_billing} & Water supply source and billing clarity. \\
\texttt{generator\_lift\_charge} & Generator and lift maintenance surcharges. \\
\texttt{maintenance\_security\_cleaning} & Building security and cleaning fees. \\
\texttt{parking} & Parking availability and charges. \\
\texttt{internet\_setup} & Internet availability and setup costs. \\
\texttt{repair\_cleaning\_paint} & Pre-move-in renovation requirements. \\
\texttt{moving\_access} & Moving van/truck access to the building. \\
\texttt{road\_access} & Road width and vehicle accessibility. \\
\texttt{waterlogging} & Monsoon flooding risk. \\
\texttt{tenant\_restriction} & Tenant type restrictions and policies. \\
\texttt{agreement\_receipt\_terms} & Rental agreement and receipt availability. \\
\texttt{rent\_increase\_terms} & Annual rent increase clauses. \\
\texttt{furnishing\_appliance\_terms} & Existing furnishing condition and terms. \\
\texttt{shared\_meter\_or\_utility} & Shared meter or utility billing risks. \\
\texttt{building\_rules} & Building-specific rules and curfews. \\
\bottomrule
\end{longtable}

\section{Status Levels}

Each scope is assigned one of:

\begin{longtable}{p{3.5cm} p{3cm} p{6.5cm}}
\toprule
\textbf{Status} & \textbf{Icon} & \textbf{Meaning} \\
\midrule
\endhead
\texttt{clear} & Green & Information is explicitly stated and unambiguous. \\
\texttt{mentioned} & Blue & Referenced in the listing but not fully detailed. \\
\texttt{missing} & Red & Critical information entirely absent. \\
\texttt{unclear} & Amber & Present but vague or contradictory. \\
\texttt{contradictory} & Purple & Multiple conflicting statements detected. \\
\texttt{not\_applicable} & Grey & Not relevant to this listing type. \\
\bottomrule
\end{longtable}

\section{Seriousness Levels}

\begin{itemize}[leftmargin=2em]
  \item \textbf{Critical} --- Can cause significant financial loss (e.g., high advance without agreement).
  \item \textbf{High} --- May lead to unexpected monthly costs (e.g., missing service charge).
  \item \textbf{Medium} --- Should be clarified but not a blocker (e.g., gas type unknown).
  \item \textbf{Low} --- Minor informational gap.
\end{itemize}

\section{Visual Representation}

The radar component renders:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Risk Ambiguity Index}: A top-level progress gauge showing overall ambiguity percentage.
  \item \textbf{Continuous Severity Sliders}: Progress bar indicators showing individual threat score levels.
  \item \textbf{Threat Status Pulses}: Animated colour-coded rings (sky, emerald, rose, amber) pulsing to indicate hazard level.
  \item \textbf{Category Breakdown}: Grouped by categories (Water Quality, Electricity, Gas Connection, Safety).
\end{itemize}

\section{Per-Scope Data}

Each detected scope provides:

\begin{itemize}[leftmargin=2em]
  \item \texttt{whyItMatters} --- Explanation of financial or safety impact.
  \item \texttt{userImpact} --- Direct impact on the user's situation.
  \item \texttt{askBeforeVisit} --- Specific questions to ask the landlord before visiting.
  \item \texttt{proofToRequest} --- Documents or evidence to request (e.g., agreement draft, service charge breakdown).
\end{itemize}


% ============================================================================
% CHAPTER 10 — AREA RECOMMENDATIONS
% ============================================================================
\chapter{Area Recommendations Engine}

\section{Overview}

The Area Recommendations engine (\filepath{components/AreaRecommendations.tsx}) suggests the best Dhaka residential areas based on the user's profile. It draws data from \filepath{lib/data/areas.ts} which contains profiles for 13 Dhaka areas.

\section{Area Profile Data}

Each area profile (\typename{AreaProfile}) contains:

\begin{longtable}{p{5cm} p{8cm}}
\toprule
\textbf{Field} & \textbf{Description} \\
\midrule
\endhead
\texttt{name} & Area name (e.g., ``Banasree'', ``Gulshan''). \\
\texttt{rentRange} & Human-readable rent range string. \\
\texttt{rentLow} / \texttt{rentHigh} & Numeric rent bounds in BDT. \\
\texttt{bestFor} & List of user types best suited (e.g., ``families'', ``bachelors''). \\
\texttt{avoidIf} & Conditions under which this area is unsuitable. \\
\texttt{commuteNotes} & Transport connectivity description. \\
\texttt{affordability} & Low / medium / high affordability rating. \\
\texttt{familySuitability} & 0--10 score for family suitability. \\
\texttt{bachelorSuitability} & 0--10 score for bachelor suitability. \\
\texttt{femaleSuitability} & 0--10 score for female tenant suitability. \\
\texttt{schoolAccess} & 0--10 score for proximity to schools. \\
\texttt{waterloggingRisk} & Low / medium / high flood risk. \\
\texttt{utilityReliability} & Low / medium / high utility service reliability. \\
\texttt{mainTradeoff} & Key compromise for this area. \\
\texttt{latitude} / \texttt{longitude} & Map coordinates for the area centre. \\
\texttt{topSchools} & Nearby prominent schools. \\
\texttt{topHospitals} & Nearby prominent hospitals. \\
\bottomrule
\end{longtable}

\section{Recommendation Algorithm}

Areas are ranked by a suitability score adjusted for the user type:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Family/Couple}: Uses \texttt{familySuitability} score.
  \item \textbf{Bachelor/Student}: Uses \texttt{bachelorSuitability} score.
  \item \textbf{Working Woman}: Uses \texttt{femaleSuitability} score.
  \item A \textbf{budget penalty} of $-5$ is applied if the area's minimum rent exceeds the user's budget.
  \item The top 4 areas are returned as recommendations.
\end{itemize}


% ============================================================================
% CHAPTER 11 — SCAN SIMULATOR
% ============================================================================
\chapter{Interactive Scan Simulator}

\section{Overview}

The Scan Simulator (\filepath{components/DemoScanAnimation.tsx}) provides a dramatic, animated radar-style scanning effect when the user initiates a search. It creates an engaging transition between profile setup and results display.

\section{Animation Stages}

The simulator progresses through sequential phases:

\begin{enumerate}[leftmargin=2em]
  \item ``Analysing commute loads...''
  \item ``Mapping waterlogging coordinates...''
  \item ``Checking hidden cost patterns...''
  \item ``Scoring household compatibility...''
  \item ``Filtering deal-breaker violations...''
  \item ``Ranking best matches...''
\end{enumerate}

Each stage includes animated counters showing:
\begin{itemize}[leftmargin=2em]
  \item Number of listings scanned.
  \item Number removed for budget mismatch.
  \item Number removed for commute mismatch.
  \item Number removed for hidden cost risks.
  \item Number removed for household mismatch.
  \item Final number of selected matches.
\end{itemize}

\section{How to Use}

\begin{enumerate}[leftmargin=2em]
  \item Select a persona or complete the wizard to create a search profile.
  \item The scan simulator activates automatically.
  \item Wait for the animation to complete (approximately 8--12 seconds).
  \item Results are displayed in the Listing Grid below.
\end{enumerate}


% ============================================================================
% CHAPTER 12 — LISTING GRID
% ============================================================================
\chapter{Scored Listing Grid}

\section{Overview}

The Listing Grid (\filepath{components/ListingGrid.tsx}) displays all scored and ranked listings in a visually rich card layout. It is the primary results view after scanning.

\section{Features}

\subsection{Listing Cards}

Each card displays:

\begin{itemize}[leftmargin=2em]
  \item Listing title and area.
  \item Monthly rent in BDT with formatting.
  \item Bedroom count, gas type, lift/generator availability.
  \item Total composite score (0--100).
  \item Verdict badge (Visit / Maybe / Call First / Avoid).
  \item ``Why it fits'' explanation text.
  \item Biggest risk warning.
  \item Image thumbnail (from DhakaImages library, seeded for consistency).
  \item Red flags and good points lists.
  \item Questions to ask the landlord.
\end{itemize}

\subsection{Comparison Selection}

Users can select up to 3 listings for side-by-side comparison by toggling the ``Compare'' checkbox on each card. The selection count is reflected in the portal tab navigation.

\subsection{Interactive Map Drawer}

Clicking ``View on Map'' opens a drawer containing a Leaflet 2D map (\filepath{components/DrawerMapInner.tsx}) showing:

\begin{itemize}[leftmargin=2em]
  \item Custom badge markers for each shortlisted listing.
  \item Badges contain rent, area name, and bedroom count.
  \item Markers are positioned using actual Dhaka coordinates from the listing data.
  \item Click interaction on markers reveals full listing details.
\end{itemize}


% ============================================================================
% CHAPTER 13 — COMPARISON MATRIX
% ============================================================================
\chapter{Side-by-Side Comparison Matrix}

\section{Overview}

The Comparison Matrix (\filepath{components/ListingComparison.tsx}) generates a detailed side-by-side specification table for up to 3 selected listings.

\section{Compared Fields}

\begin{multicols}{2}
\begin{itemize}[leftmargin=1em]
  \item Monthly rent
  \item Total first-month cost
  \item Advance months
  \item Service charge
  \item Broker fee
  \item Bedrooms / Bathrooms
  \item Gas type
  \item Lift availability
  \item Generator backup
  \item Waterlogging risk
  \item Tenant preference
  \item Area
  \item Composite score
  \item Verdict
\end{itemize}
\end{multicols}

\section{Highlight Badges}

The comparison automatically identifies and highlights:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Cheapest Rent} --- The listing with the lowest monthly rent.
  \item \textbf{Lowest Upfront Cash} --- The listing with the lowest total first-month cost.
  \item \textbf{Best Commute} --- The listing with the highest commute fit score.
\end{itemize}

\section{Visit Order Sorting}

Listings are ranked by their composite score and assigned a visit order:

\begin{itemize}[leftmargin=2em]
  \item \textbf{\#1 Visit First} --- Highest scored listing. This element functions as a clickable button that navigates the user to the Visit Preparation Workspace at \texttt{/portal/visit}.
  \item \textbf{\#2 Visit 2nd} --- Second-highest scored listing.
  \item \textbf{\#3 Visit 3rd} --- Third-highest scored listing.
\end{itemize}


% ============================================================================
% CHAPTER 14 — VISIT PREPARATION WORKSPACE
% ============================================================================
\chapter{Visit Preparation Workspace}

\section{Overview}

The Visit Preparation Workspace (\filepath{components/VisitPlanner.tsx}) is a comprehensive multi-tab preparation toolkit accessed at \texttt{/portal/visit}. It provides everything a renter needs before, during, and after visiting a flat.

\section{Tab 1: Calling Script Customiser}

\subsection{Pre-Loaded Scripts}

The workspace generates pre-written Banglish phone call dialogues tailored to the matched listing parameters. The scripts cover:

\begin{itemize}[leftmargin=2em]
  \item Introducing yourself and stating interest.
  \item Asking about service charge breakdown.
  \item Confirming gas type (line vs cylinder).
  \item Negotiating advance months.
  \item Asking about broker fees.
  \item Confirming tenant preference policies.
  \item Asking about parking, generator, and lift.
  \item Requesting a visit appointment.
\end{itemize}

\subsection{Rich Text Editing}

The script is fully editable with a formatting action bar:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Bold} --- Apply bold formatting to selected text.
  \item \textbf{Italics} --- Apply italic formatting.
  \item \textbf{Underline} --- Apply underline formatting.
  \item \textbf{Template Reset} --- Reset the script to the original auto-generated template.
  \item \textbf{Save/Edit Toggle} --- Switch between editing and read-only modes.
\end{itemize}

The editor uses \texttt{document.execCommand} for inline formatting and \texttt{contentEditable} divs for the editing surface.

\subsection{How to Use}

\begin{enumerate}[leftmargin=2em]
  \item Navigate to \texttt{/portal/visit} (or click ``\#1 Visit First'' from the comparison table).
  \item Review the auto-generated calling script.
  \item Click ``Edit'' to modify the script. Add or remove questions as needed.
  \item Use the formatting toolbar to highlight important points.
  \item Click ``Save'' to lock the script for reference during the call.
\end{enumerate}

\section{Tab 2: Physical Inspection Blueprint}

\subsection{Interactive Checklists}

The inspection blueprint provides two pre-populated checklist categories:

\begin{enumerate}[leftmargin=2em]
  \item \textbf{Utilities \& Hardware}:
  \begin{itemize}
    \item Water pressure check (all taps).
    \item Electricity meter type (shared/private, prepaid/postpaid).
    \item Gas connection verification.
    \item Generator/IPS backup test.
    \item Lift functionality test.
    \item Fan, light, and socket verification.
  \end{itemize}

  \item \textbf{Neighbourhood \& Building Environment}:
  \begin{itemize}
    \item Street width and vehicle access.
    \item Nearest hospital and pharmacy distance.
    \item Guard presence and night security.
    \item Floor height and ventilation.
    \item Natural light from windows.
    \item Nearby mosque/market proximity.
    \item Drainage and waterlogging signs.
  \end{itemize}
\end{enumerate}

\subsection{Square Checkbox Notes}

All checklist items use \textbf{square-shaped checkboxes} (via CSS \texttt{appearance: none} with custom borders) so users clearly identify them as checkable inspection notes.

\subsection{Drag-and-Drop Reordering}

Users can \textbf{drag and drop} checklist items to reorder them according to their visit plan. The implementation uses native HTML5 drag-and-drop with:

\begin{itemize}[leftmargin=2em]
  \item Drag handles on each item.
  \item Visual highlight overlays during the drag operation.
  \item Automatic re-indexing after drops.
\end{itemize}

\subsection{Custom Checkpoint Addition}

A form at the bottom of each checklist section allows users to \textbf{add their own checkpoints}. Users type a new item label and description, then click ``Add'' to append it to the list.

\section{Tab 3: Landlord Negotiation Playbook}

Information cards detailing guidelines on:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Curfews \& Gate Access} --- Understanding building gate closing times and late-night entry policies.
  \item \textbf{Security Deposits} --- How to handle, negotiate, and document advance payments.
  \item \textbf{Service Charges} --- What should and should not be included in the service charge.
  \item \textbf{Maintenance Duties} --- Clarifying who is responsible for repairs, painting, and appliance maintenance.
  \item \textbf{Monthly Official Receipts} --- Insisting on rent receipts for legal protection.
\end{itemize}

\section{Tab 4: Listing Creation Factors}

Guidelines for tenants who are also creating their own listing:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Flat Orientation} --- Valuing south/east-facing flats for wind flow and natural light.
  \item \textbf{Gas Type Importance} --- Always specifying whether gas is pipeline or cylinder.
  \item \textbf{Notice Period} --- Standard practices for giving and receiving notice.
  \item \textbf{Tenant Matching Constraints} --- How to specify tenant preferences clearly without discrimination.
  \item \textbf{Photography Tips} --- What angles and rooms to photograph for effective listings.
\end{itemize}


% ============================================================================
% CHAPTER 15 — ASSESSMENT REPORT
% ============================================================================
\chapter{Comprehensive Assessment Report}

\section{Overview}

The Assessment Report (\filepath{components/ReportPreview.tsx}) compiles a comprehensive, print-ready summary of the entire house-hunting session.

\section{Report Sections}

\subsection{Plan Summary Overview}

\begin{itemize}[leftmargin=2em]
  \item Renter profile summary (household type, budget, commute anchors).
  \item Search parameters and deal-breakers.
  \item Total listings scanned and filtered.
  \item Number of shortlisted matches.
\end{itemize}

\subsection{Recommended Areas}

\begin{itemize}[leftmargin=2em]
  \item Top 4 recommended areas with rent ranges.
  \item Suitability scores and trade-offs.
  \item Commute connectivity notes.
\end{itemize}

\subsection{Shortlisted Listings \& Visit Order}

\begin{itemize}[leftmargin=2em]
  \item Ranked list of selected listings with scores.
  \item Recommended visit order (1st, 2nd, 3rd).
  \item Per-listing summary including rent, area, verdict, and biggest risk.
\end{itemize}

\subsection{Printable Output}

The report can be printed or saved as PDF. It aggregates:

\begin{itemize}[leftmargin=2em]
  \item Visit checklists from the inspection blueprint.
  \item Warning parameters and red flags.
  \item Phone script transcripts.
  \item Hidden cost scope summaries.
  \item First-month cost breakdowns for each listing.
\end{itemize}


% ============================================================================
% CHAPTER 16 — DATA HARVESTER PIPELINE
% ============================================================================
\chapter{Data Harvester Pipeline}

\section{Overview}

The harvester pipeline (\filepath{lib/harvester/}) is a modular data ingestion and processing system that feeds fresh listing data into BasaBondhu's matching engine. It runs server-side through API routes at \apiendpoint{/api/harvester/}.

\section{Pipeline Components}

\begin{longtable}{p{6cm} p{7cm}}
\toprule
\textbf{Service} & \textbf{Responsibility} \\
\midrule
\endhead
\texttt{harvester-orchestrator} & Coordinates the full pipeline: ingest $\to$ normalise $\to$ extract $\to$ score $\to$ publish. \\
\midrule
\texttt{source-registry} & Manages and registers data source configurations. \\
\midrule
\texttt{raw-document} & Handles raw document storage and retrieval. \\
\midrule
\texttt{text-normalizer} & Cleans and normalises raw Bangla/Banglish text. \\
\midrule
\texttt{chunk-builder} & Splits large documents into processable chunks. \\
\midrule
\texttt{extractor} & Regex-based field extraction from chunks. \\
\midrule
\texttt{openrouter-extractor} & AI-powered extraction via OpenRouter API for complex listings. \\
\midrule
\texttt{enrichment} & Enriches extracted data with area metadata and coordinates. \\
\midrule
\texttt{quality} & Quality scoring and validation of extracted listings. \\
\midrule
\texttt{dedupe} & Deduplication of listings by title and content similarity. \\
\midrule
\texttt{freshness} & Tracks listing freshness and expiry dates. \\
\midrule
\texttt{structured-listing-builder} & Builds final structured listing objects from extracted data. \\
\midrule
\texttt{offer-snapshot} & Creates point-in-time snapshots of listing offers. \\
\midrule
\texttt{listing-mapper} & Maps harvested listing format to the application's \typename{Listing} type. \\
\midrule
\texttt{google-sheet-importer} & Imports listings from Google Sheets. \\
\midrule
\texttt{partner-csv-importer} & Imports listings from partner CSV files. \\
\midrule
\texttt{public-url-ingestion} & Ingests listings from public URLs. \\
\midrule
\texttt{user-paste-ingestion} & Processes user-pasted raw text through the pipeline. \\
\bottomrule
\end{longtable}


% ============================================================================
% CHAPTER 17 — API ROUTES
% ============================================================================
\chapter{API Routes}

\section{Overview}

All API routes are implemented as Next.js App Router route handlers under \filepath{app/api/}.

\begin{longtable}{p{5cm} p{2cm} p{6cm}}
\toprule
\textbf{Endpoint} & \textbf{Method} & \textbf{Description} \\
\midrule
\endhead
\texttt{/api/areas} & GET & Returns all 13 Dhaka area profiles. \\
\midrule
\texttt{/api/listings} & GET & Returns all seed listings. \\
\midrule
\texttt{/api/search} & POST & Creates a search profile and returns scored listings. \\
\midrule
\texttt{/api/parse} & POST & Parses raw listing text and returns structured fields. \\
\midrule
\texttt{/api/facebook/fetch} & POST & Crawls a Facebook URL and returns raw caption text. \\
\midrule
\texttt{/api/compare} & POST & Computes comparison result for selected listings. \\
\midrule
\texttt{/api/report} & POST & Generates a full housing assessment report. \\
\midrule
\texttt{/api/demo} & GET & Returns demo scan animation data. \\
\midrule
\texttt{/api/harvester/*} & Various & Harvester pipeline endpoints for data ingestion. \\
\bottomrule
\end{longtable}


% ============================================================================
% CHAPTER 18 — TYPE SYSTEM
% ============================================================================
\chapter{Type System}

\section{Overview}

The entire application is strictly typed using TypeScript. Core type definitions are in \filepath{lib/types.ts} with domain-specific types in \filepath{lib/domain/} and \filepath{lib/types/}.

\section{Core Types}

\subsection{SearchProfile}

The central data structure representing a user's renter profile:

\begin{lstlisting}[language=Java, caption={SearchProfile Type}]
type SearchProfile = {
  id: string;
  mode: "plan" | "check" | "compare" | "visit";
  rentingOrBuying: "renting" | "buying";
  householdType: HouseholdType;
  lookingFor: "full-flat" | "room-sublet" | "checking-listing";
  budgetMonthly: number;
  maxFirstMonthCash: number;
  commuteAnchors: { label: string; area: string }[];
  priorities: Priority[];
  dealBreakers: DealBreaker[];
  hiddenCostSensitivity?: HiddenCostSensitivity;
  // Optional fields for advanced matching
  husbandJobLocation?: string;
  wifeJobLocation?: string;
  childSchoolLocation?: string;
  needsHealthcare?: boolean;
  ownsCar?: boolean;
  preferredFacing?: "south" | "east" | "west" | "north" | "any";
  wantsNearbyMarket?: boolean;
  environmentPreference?: "quiet" | "commercial" | "any";
};
\end{lstlisting}

\subsection{Listing}

Represents a single rental listing with 30+ fields covering location, pricing, amenities, risks, and metadata. Key fields include:

\begin{itemize}[leftmargin=2em]
  \item \texttt{id}, \texttt{title}, \texttt{rawText}, \texttt{sourceType}
  \item \texttt{area}, \texttt{addressHint}, \texttt{latitude}, \texttt{longitude}
  \item \texttt{rent}, \texttt{bedrooms}, \texttt{bathrooms}, \texttt{sizeSqft}
  \item \texttt{tenantPreference}, \texttt{familyAllowed}, \texttt{bachelorAllowed}
  \item \texttt{advanceMonths}, \texttt{brokerFee}, \texttt{serviceCharge}
  \item \texttt{gasType}, \texttt{lift}, \texttt{generator}
  \item \texttt{waterloggingRisk}, \texttt{utilityClarity}
  \item \texttt{commuteNotes}, \texttt{houseRules}, \texttt{redFlags}, \texttt{goodPoints}
  \item \texttt{hiddenCostSignals}
\end{itemize}

\subsection{ScoredListing}

Extends \typename{Listing} with:

\begin{itemize}[leftmargin=2em]
  \item \texttt{scores} --- Object containing all 9 individual score components plus total.
  \item \texttt{hiddenCostScopes} --- Array of detected hidden cost sources.
  \item \texttt{verdict} --- Final verdict (visit/maybe/call-first/avoid).
  \item \texttt{whyItFits} --- Human-readable suitability explanation.
  \item \texttt{biggestRisk} --- Primary risk factor description.
  \item \texttt{questionsToAsk} --- Array of questions for the landlord.
\end{itemize}

\subsection{Other Types}

\begin{itemize}[leftmargin=2em]
  \item \typename{ParsedListing} --- Output of the text parser with extracted fields and confidence level.
  \item \typename{AreaProfile} --- Complete area metadata including suitability scores and hidden cost profiles.
  \item \typename{FirstMonthCost} --- Cost breakdown with warnings.
  \item \typename{ComparisonResult} --- Comparison output with rankings and best-of badges.
  \item \typename{ChecklistSection} --- Inspection checklist category and items.
  \item \typename{HousingReport} --- Complete assessment report data structure.
  \item \typename{ScanSummary} --- Scan statistics (scanned, removed by category, selected).
  \item \typename{HiddenCostSource} --- Individual hidden cost detection with metadata.
\end{itemize}


% ============================================================================
% CHAPTER 19 — UI COMPONENTS
% ============================================================================
\chapter{UI Components Library}

\section{Navbar}

\filepath{components/Navbar.tsx} --- Sticky top navigation bar with:
\begin{itemize}[leftmargin=2em]
  \item Brand logo and name.
  \item Navigation links to portal sections.
  \item Responsive mobile menu.
  \item Glassmorphism backdrop blur effect.
\end{itemize}

\section{ErrorBoundary}

\filepath{components/ErrorBoundary.tsx} --- React class-based error boundary that:
\begin{itemize}[leftmargin=2em]
  \item Catches JavaScript errors in child components.
  \item Renders a fallback UI with an error title and reset button.
  \item Logs error details to the console.
\end{itemize}

\section{Typewriter}

\filepath{components/Typewriter.tsx} --- Character-by-character typing animation effect used for dynamic text reveals.

\section{Skeletons}

\filepath{components/Skeletons.tsx} --- Loading skeleton placeholder components that render grey pulsing shapes matching the final content layout. Used during data loading states.

\section{PersonaIcons}

\filepath{components/PersonaIcons.tsx} --- Custom SVG icon set for each renter persona type:
\begin{itemize}[leftmargin=2em]
  \item Couple icon
  \item Student icon
  \item Professional icon
  \item Family icon
  \item Executive icon
  \item Group icon
\end{itemize}

\section{HousingProfileSummary}

\filepath{components/HousingProfileSummary.tsx} --- Compact summary card displaying the active search profile's key parameters (household type, budget, area, priorities).

\section{ProofRequestPanel}

\filepath{components/ProofRequestPanel.tsx} --- UI panel that displays a list of documents and proofs to request from the landlord/broker based on detected hidden cost scopes.

\section{ModeSelector}

\filepath{components/ModeSelector.tsx} --- Selection interface for choosing the analysis mode (Plan / Check / Compare / Visit).


% ============================================================================
% CHAPTER 20 — SERVICE LAYER
% ============================================================================
\chapter{Service Layer}

\section{Overview}

The service layer (\filepath{lib/services/}) contains 13 specialised service modules that encapsulate business logic.

\begin{longtable}{p{6cm} p{7cm}}
\toprule
\textbf{Service} & \textbf{Purpose} \\
\midrule
\endhead
\texttt{area-recommendation} & Computes area suitability rankings based on user profile. \\
\midrule
\texttt{checklist} & Generates inspection checklists tailored to listing parameters. \\
\midrule
\texttt{compare} & Produces side-by-side comparison data with rankings and badges. \\
\midrule
\texttt{cost} & Calculates first-month costs and generates financial warnings. \\
\midrule
\texttt{demo-scan} & Generates scan summary statistics for the animation. \\
\midrule
\texttt{hidden-cost-scope} & Detects and classifies all hidden cost scopes in a listing. \\
\midrule
\texttt{listing-parser} & Synchronous wrapper around the text parser for scoring use. \\
\midrule
\texttt{openrouter} & Interfaces with the OpenRouter AI API for enhanced text processing. \\
\midrule
\texttt{question} & Generates context-specific questions to ask landlords. \\
\midrule
\texttt{recommendation} & Computes listing recommendation scores and explanations. \\
\midrule
\texttt{report} & Assembles the full housing assessment report data structure. \\
\midrule
\texttt{scoring} & Orchestrates the multi-factor scoring algorithm. \\
\midrule
\texttt{search-profile} & Validates and normalises search profile inputs. \\
\bottomrule
\end{longtable}


% ============================================================================
% CHAPTER 21 — PORTAL NAVIGATION
% ============================================================================
\chapter{Portal Navigation}

\section{Tab Structure}

The portal (\filepath{app/portal/layout.tsx}) provides a persistent tab navigation bar with 6 tabs:

\begin{longtable}{p{1cm} p{3.5cm} p{3cm} p{5cm}}
\toprule
\textbf{\#} & \textbf{Tab Label} & \textbf{Route} & \textbf{Component} \\
\midrule
\endhead
1 & Plan Search & \texttt{/portal} & Portal main page with personas and scan. \\
2 & Check Listing & \texttt{/portal/parser} & ListingChecker component. \\
3 & Facebook Fetcher & \texttt{/portal/fb-fetch} & FacebookFetcher component. \\
4 & Compare Homes & \texttt{/portal/compare} & ListingComparison component. \\
5 & Prepare Visit & \texttt{/portal/visit} & VisitPlanner component. \\
6 & Report & \texttt{/portal/report} & ReportPreview component. \\
\bottomrule
\end{longtable}

\section{Navigation Features}

\begin{itemize}[leftmargin=2em]
  \item Active tab highlighting with primary colour background and shadow.
  \item Horizontal scroll on mobile for tab overflow.
  \item Comparison count badge dynamically updated (e.g., ``Compare Homes (2)'').
  \item Lucide React icons for each tab.
  \item Sticky positioning below the main navbar.
  \item Glassmorphism backdrop with blur effect.
  \item Page transition animation (fade-in) on tab switch.
\end{itemize}


% ============================================================================
% CHAPTER 22 — DESIGN SYSTEM
% ============================================================================
\chapter{Design System}

\section{Colour Palette}

\begin{longtable}{p{4cm} p{4cm} p{5cm}}
\toprule
\textbf{Token} & \textbf{Value} & \textbf{Usage} \\
\midrule
\endhead
\texttt{--primary} & \texttt{\#C9952B} (Gold) & Brand accents, CTAs, highlights. \\
\texttt{--bg} & \texttt{\#FAFAF8} & Main background. \\
\texttt{--bg-alt} & \texttt{\#F5F3EE} & Alternate section backgrounds. \\
\texttt{--text-main} & \texttt{\#1A1A2E} & Primary text colour. \\
\texttt{--text-muted} & \texttt{\#6B7280} & Secondary/muted text. \\
\texttt{--visit} & Green tones & ``Visit'' verdict indicators. \\
\texttt{--maybe} & Amber tones & ``Maybe'' verdict indicators. \\
\texttt{--call-first} & Orange tones & ``Call First'' verdict indicators. \\
\texttt{--avoid} & Red tones & ``Avoid'' verdict indicators. \\
\bottomrule
\end{longtable}

\section{Typography}

\begin{itemize}[leftmargin=2em]
  \item \textbf{Inter} (\texttt{--font-inter}): Primary sans-serif for UI text, labels, and body copy.
  \item \textbf{Cormorant Garamond} (\texttt{--font-cormorant}): Serif font for hero headings and cinematic text.
\end{itemize}

\section{Animation System}

\begin{itemize}[leftmargin=2em]
  \item \texttt{animate-fade-in}: 0.25s ease-out opacity transition for page entries.
  \item Framer Motion used for complex animations: scan radar, card reveals, page transitions, and micro-interactions.
  \item CSS transitions (300ms duration) for colour changes, hover effects, and layout shifts.
  \item Active scale effects (\texttt{active:scale-95}) on interactive elements for tactile feedback.
\end{itemize}

\section{Responsive Design}

All components use Tailwind CSS responsive prefixes:
\begin{itemize}[leftmargin=2em]
  \item \texttt{sm:} --- 640px+ (tablet portrait).
  \item \texttt{md:} --- 768px+ (tablet landscape).
  \item \texttt{lg:} --- 1024px+ (desktop).
  \item \texttt{xl:} --- 1280px+ (wide desktop).
\end{itemize}


% ============================================================================
% CHAPTER 23 — CONFIGURATION
% ============================================================================
\chapter{Configuration \& Environment}

\section{Environment Variables}

The application uses a \filepath{.env.local} file for sensitive configuration. Key variables include:

\begin{itemize}[leftmargin=2em]
  \item API keys for OpenRouter AI service.
  \item Database connection strings (if applicable).
  \item Feature flags for experimental features.
\end{itemize}

\section{TypeScript Configuration}

\filepath{tsconfig.json} configures:
\begin{itemize}[leftmargin=2em]
  \item Path aliases: \texttt{@/*} maps to the project root.
  \item Strict mode enabled for type safety.
  \item ES2017+ target for modern JavaScript features.
  \item JSX preserve mode for Next.js compilation.
\end{itemize}

\section{Next.js Configuration}

\filepath{next.config.ts} configures:
\begin{itemize}[leftmargin=2em]
  \item Image optimisation settings.
  \item Custom headers for API routes.
  \item Build optimisation flags.
\end{itemize}

\section{ESLint Configuration}

\filepath{eslint.config.mjs} extends \texttt{eslint-config-next} for Next.js-specific linting rules.


% ============================================================================
% CHAPTER 24 — RUNNING THE PROJECT
% ============================================================================
\chapter{Running the Project}

\section{Prerequisites}

\begin{itemize}[leftmargin=2em]
  \item Node.js 18+ installed.
  \item npm 9+ installed.
  \item Git for version control.
\end{itemize}

\section{Installation}

\begin{lstlisting}[language=bash, caption={Installation Commands}]
# Clone the repository
git clone <repository-url>
cd Bashabondhu/basabondhu

# Install dependencies
npm install

# Create environment file
cp .env.example .env.local
# Edit .env.local with your API keys
\end{lstlisting}

\section{Development}

\begin{lstlisting}[language=bash, caption={Development Server}]
# Start the development server
npm run dev

# The app will be available at http://localhost:3000
\end{lstlisting}

\section{Production Build}

\begin{lstlisting}[language=bash, caption={Production Build}]
# Build for production
npm run build

# Start the production server
npm start
\end{lstlisting}

\section{Available Scripts}

\begin{longtable}{p{4.5cm} p{8.5cm}}
\toprule
\textbf{Script} & \textbf{Description} \\
\midrule
\endhead
\texttt{npm run dev} & Start the Next.js development server with hot reload. \\
\texttt{npm run build} & Create an optimised production build. \\
\texttt{npm start} & Start the production server. \\
\texttt{npm run lint} & Run ESLint checks across the codebase. \\
\texttt{npm run clean} & Delete the \texttt{.next} cache directory. \\
\texttt{npm run clean-root-lock} & Remove the root-level \texttt{package-lock.json}. \\
\bottomrule
\end{longtable}


% ============================================================================
% CHAPTER 25 — GLOSSARY
% ============================================================================
\chapter{Glossary}

\begin{longtable}{p{4cm} p{9cm}}
\toprule
\textbf{Term} & \textbf{Definition} \\
\midrule
\endhead
BasaBondhu & ``House Friend'' in Bangla. The platform name. \\
\midrule
Banglish & A mix of Bangla and English commonly used in Dhaka social media. \\
\midrule
Service Charge & Monthly building maintenance fee covering security, cleaning, lift operation, and common area utilities. \\
\midrule
Advance & Upfront security deposit, typically 1--3 months of rent, paid before moving in. \\
\midrule
Line Gas & Government Titas gas pipeline connection (cheaper, reliable). \\
\midrule
Cylinder Gas & LPG cylinder gas (more expensive, requires regular refills). \\
\midrule
Broker Fee & One-time commission paid to a housing broker/agent, typically 50--100\% of one month's rent. \\
\midrule
Waterlogging & Street-level flooding common in low-lying Dhaka areas during monsoon season. \\
\midrule
Commute Anchor & A location the user commutes to daily (office, university, school). \\
\midrule
Deal Breaker & A hard disqualifier that automatically rejects a listing regardless of other scores. \\
\midrule
Hidden Cost Scope & A category of potentially hidden, missing, or unclear financial information in a listing. \\
\midrule
Verdict & The final recommendation for a listing: visit, maybe, call-first, or avoid. \\
\midrule
Harvester & The backend data pipeline that ingests, normalises, and publishes fresh listing data. \\
\midrule
Persona & A pre-built renter profile representing a common Dhaka house-hunter archetype. \\
\bottomrule
\end{longtable}


% ============================================================================
% APPENDIX
% ============================================================================
\appendix

\chapter{Supported Dhaka Areas}

The following 13 Dhaka metropolitan areas are supported with full profile data, commute matrices, and listing coverage:

\begin{multicols}{2}
\begin{enumerate}[leftmargin=2em]
  \item Banasree
  \item Badda
  \item Merul Badda
  \item Mohakhali
  \item Tejgaon
  \item Mohammadpur
  \item Lalmatia
  \item Mirpur
  \item Uttara
  \item Bashundhara
  \item Dhanmondi
  \item Banani
  \item Gulshan
\end{enumerate}
\end{multicols}

\chapter{Commute Compatibility Matrix}

The following matrix shows inter-area commute compatibility scores (0--100 scale). Higher scores indicate better connectivity.

\begin{table}[H]
\centering
\footnotesize
\caption{Commute Matrix (Selected Areas)}
\begin{tabular}{l|c c c c c c}
\toprule
& \textbf{Banasree} & \textbf{Badda} & \textbf{Mohakhali} & \textbf{Mirpur} & \textbf{Uttara} & \textbf{Gulshan} \\
\midrule
Banasree & 100 & 80 & 60 & 30 & 30 & 70 \\
Badda & 80 & 100 & 75 & 40 & 50 & 85 \\
Mohakhali & 60 & 75 & 100 & 60 & 70 & 85 \\
Mirpur & 30 & 40 & 60 & 100 & 65 & 55 \\
Uttara & 30 & 50 & 70 & 65 & 100 & 60 \\
Gulshan & 70 & 85 & 85 & 55 & 60 & 100 \\
\bottomrule
\end{tabular}
\end{table}


\chapter{Scoring Weight Distribution}

\begin{table}[H]
\centering
\caption{Default Scoring Weights}
\begin{tabular}{l c}
\toprule
\textbf{Factor} & \textbf{Default Weight} \\
\midrule
Budget Fit & 25\% \\
Commute Fit & 20\% \\
Household Fit & 15\% \\
Hidden Cost Penalty & 15\% \\
First Month Fit & 10\% \\
Utility Clarity & 5\% \\
Waterlogging Risk & 5\% \\
Listing Trust & 5\% \\
\midrule
\textbf{Total} & \textbf{100\%} \\
\bottomrule
\end{tabular}
\end{table}


% ============================================================================
\end{document}
